\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

\medskip
The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media. The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

>>>>

\medskip
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is \red{XX} $\times$ \red{XX} unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also includes no-flux across upper and lower boundaries. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).

Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{evans_1994} \citep[see also][]{dawe_2008}.

The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

%%%%
%%%%  FIGURE 4
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{0.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}
\clearpage

>>>>

%%%%
%%%%  FIGURE 4
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilities ($\mathbf{K}$)
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  \red{(Is this time or the vtu number ??)}
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) flow at t=3000  
}
}     
\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at \red{t=XX} and \red{t=XX}. The domain is discretised in \red{XX} \PN[1]{2} elements. \red{(ALSO YOU MUST ADD SATURATION LEGENDS IN ALL FIGURES.)}}
\label{fem_cv_represent_a}
\end{figure}
\clearpage
